A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-06-07 main.tex
Wrote a paragraph of ベクトル計算も高速化できる.

\subsubsection{行列計算も高速化できる}

Multistage calculi can also optimize matrices calculation.

>>>>

% \subsubsection{ベクトル計算も高速化できる}

Multistage programming can also optimize vector calculation.
For example, an add function of two vectors is impremented with loop in many cases
though it is used very often in programs handling vectors.
We can unrolling an add function and optimize it with multistage programming.
